Refinements for open automata

### 2023-03-09 2021-Refinement/paper/refinementarticleV2.tex
point dsicute ce matin with no change
new proof sketch

Moreover, we have  for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ the following:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
\end{multline*}

@@

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions as $A_1$ (up to renaming) as those used to build $t_{12}$.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have:
\begin{align*}
  J'_{13x} \cap H'  
&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{12} \cap H'
\end{align*}

@@

Moreover, we have  for any transition $t_1 $ in $A_1$ relying $s_3$ and $s^{\prime}_1$ the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

@@

\paragraph{Second case: Only the encompassing automaton performs a transition.}
  $t_{12}$ is obtained by the transition 
$\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
\]
As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
 with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]

$\forall x \in X$ we have
\begin{align*}		
J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
& = \mpar{J'_{12}\cap H' }
\end{align*}

\medskip
\TODO{To check form this point}

We have for all $\mpar{s_{2}, s_{3}} \in S_{2} \times S_{3}$ such that $\reach{A_{12}}(s_{12})$ is satisfiable:
\begin{align*}
 R\mpar{s_{2}, s_{3}} &\implies  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \\
 & \implies
R' \mpar{s_{12}, s_{13}}
\end{align*}

Since in this case the state $s'_{12}$ is the same as $s_{12}$ and $s'_{13x}$ is the same as $s_{13}$, we get:
\begin{align*}
 R\mpar{s_{2}, s_{3}}  & \implies
R' \mpar{s_{12}, s_{13}}\\
& \implies
R' \mpar{s'_{12}, s'_{13x}}
\end{align*}
Furthermore for this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12}$ is the same as $ g^1_1$, $g_{13x}$    as $g^2_1$, $\alpha_{12}$ as $\alpha^1_1$ and $\alpha_{23x}$ as  $\alpha^2_1$.  Similarly, 
$\beta_{13j}$ and $\beta_{23xj}$ are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.\\

Moreover, we have  for any transition $t_1$ in $A_1$ that is used to build $t_{12}$ and $t_{13x}$ the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

From the above we can deduce the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}}   
\end{multline*}

>>>>

Moreover, we have  for any transition $t_3$ in $A_3$ relating $s_3$ and $s^{\prime}_3$ the following:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
\end{multline*}

@@

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transition, up to renaming, as the one used to build $t_{12}$ (i.e. $t_1^1$), where ${s^2_{1}}^\prime$ is the same as ${s^1_{1}}^\prime$ up to renaming.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have:
\begin{align*}
  J'_{13x} \cap H'  
&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{12} \cap H'
\end{align*}

@@

Moreover, we have  for any transition $t_1 $ in $A_1$ relating $s^1_1$ and ${s^1_1}^{\prime}$ the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

@@

\paragraph{Second case: Only the encompassing automaton performs a transition.}
  $t_{12}$ is obtained by the transition 
$\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
\]
%As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
% with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
%produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
%\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]

\TODO{NEW -- a refaire en plus joli}

Because the hole is not involved we can define (where elements of $A_1$ are the same as above modulo renaming of variables):
\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1}
\]

% 
%$\forall x \in X$ we have
%\begin{align*}		
%J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
%& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
%& = \mpar{J'_{12}\cap H' }
%\end{align*}

We have by definition 
\[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
Thus, because transitions are the same:
\[R' \mpar{s_{12}, s_{13}} \implies
R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime
\]

Moreover, we have  the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

 Furthermore, according to the Definition \ref{Def:Reach} (reachability, applied to the composed automaton \(A_1\)) we have, for all $t_{12} \in T_{12}$:
\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]

From the above we can deduce the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
			 R'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
		\end{array}}   
\end{multline*}
